---
title: "Creating a custom plot of raster data with a vector overlay"
output: html_document
---
This tutorial covers the concept and the coding of a function the creates a plot of a raster with a vector dataset as an overlay.

##Preperation
Several libraries are needed for this project:
```{r, message=FALSE, warning=FALSE}
library(raster)
library(sp)
library(rgdal)
library(latticeExtra)
```
Using the functionality of the imported libraries, the input datasets are loaded as individual objects:
```{r, message=FALSE, warning=FALSE, results='hide'}
raster <- raster("D:\\Studium (EnvGEo)\\Erstes_Semester\\Data_Management\\Datasets\\fogo_landsat_2014-11-24\\LC82100502014328LGN00_B3.tif")
vector <- readOGR("D:\\Studium (EnvGEo)\\Erstes_Semester\\Data_Management\\Datasets\\fogo_field_survey_2014\\data_2014_subset1.shp", layer = "data_2014_subset1")
```
##Function
The final function is of this structure: 
```{r, eval=F}
custom_map <- function(raster, vector, v.attr, v.breaks, v.color="Greens")
```
It takes as parameters the raster object `raster`, the vector object `vector` and some configuration parameters:
  + `v.attr` - The attribute of the vector used for classification
  + `v.breaks` - A vector containing the break values of the classes
  + `v.color` - The color of the vector visualization (default = "Greens")
  
###Code sections
At first, the projection of the two inputs has to be equal. Therefore, the projection of the vector data is adapted if needed:
```{r, eval=F}
   if (projection(raster) != projection(vector)) {
    vector <- spTransform(vector, CRS(projection(raster)))
  }

```
Breaks based on the standart deviation are computed to be used for a contrast stretch when plotting the raster:
```{r, eval=F}
  min <- max(mean(getValues(raster)) - sd(getValues(raster)), 0)
  max <- mean(getValues(raster)) + sd(getValues(raster))
  
  breaks <- seq(min, max, length.out = 256)

```
The plot features a coordinate grid. The equally spaced steps are created like this:
```{r, eval=F}
  yat = seq(extent(raster)@ymin, 
            extent(raster)@ymax, length.out = 5)
  xat = seq(extent(raster)@xmin, 
            extent(raster)@xmax, length.out = 5)

```
Variables for the vector classification are established. This includes classes and colors:
```{r, eval=F}
  vector_classes <- cut(vector@data[,colnames(vector@data) == v.attr], v.breaks)
  vector_colors <- colorRampPalette(brewer.pal(6,v.color))(6)

```
The raster plot is set up by a call of the function `spplot`. The coordinate grid is included via the parameter `panel` and its values are printed to the axis via the parameter `scales`. What is returned by the function gets stored in the variable `plt`:
```{r, eval=F}
  plt <- spplot(raster, col.regions = gray.colors(256), at = breaks,
                key = list(space = 'left', text = list(levels(vector_classes)), 
                           points = list(pch = 21, cex = 2, fill = vector_colors)),
                colorkey=list(space="right"),
                panel = function(...){
                  panel.levelplot(...)
                  panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
                },
                scales = list(x = list(at = xat),
                              y = list(at = yat)))

```
The vector plot is set up by a second call of the function `spplot`. Information about the classification and color is inputted by the variables defined above. What is returned by the function gets stored in the variable `orl`:
```{r, eval=F}
  orl <- spplot(vector, zcol = v.attr, col.regions = vector_colors, 
                cuts = v.breaks)

```
Both plot objects are combined and the plot is created:
```{r, eval=F}
  plt + as.layer(orl)

```
##Final Result
All sections are now combined and put into the framework of the funtion:
```{r, echo=T}
custom_map <- function(raster, vector, v.attr, v.breaks, v.color="Greens"){
 
   if (projection(raster) != projection(vector)) {
    vector <- spTransform(vector, CRS(projection(raster)))
  }
  
  min <- max(mean(getValues(raster)) - sd(getValues(raster)), 0)
  max <- mean(getValues(raster)) + sd(getValues(raster))
  
  breaks <- seq(min, max, length.out = 256)
  
  yat = seq(extent(raster)@ymin, 
            extent(raster)@ymax, length.out = 5)
  xat = seq(extent(raster)@xmin, 
            extent(raster)@xmax, length.out = 5)
  
  vector_classes <- cut(vector@data[,colnames(vector@data) == v.attr], v.breaks)
  vector_colors <- colorRampPalette(brewer.pal(6,v.color))(6)
  
  plt <- spplot(raster, col.regions = gray.colors(256), at = breaks,
                key = list(space = 'left', text = list(levels(vector_classes)), 
                           points = list(pch = 21, cex = 2, fill = vector_colors)),
                colorkey=list(space="right"),
                panel = function(...){
                  panel.levelplot(...)
                  panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
                },
                scales = list(x = list(at = xat),
                              y = list(at = yat)))
  
  orl <- spplot(vector, zcol = v.attr, col.regions = vector_colors, 
                cuts = v.breaks)
  
  plt + as.layer(orl)
  
}
```

The function is called with valid parameter values and the plot gets created:
```{r, echo=T}
custom_map(raster = raster, vector = vector, v.attr = "NAT", v.breaks = c(0, 20, 40, 60, 80, 100, 120), v.color="Reds")
```

