---
title: "Worksheet12-1"
author: "Luise Wraase"
date: "26. Januar 2016"
output: html_document
runtime: shiny
---

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.




```{r,message=FALSE, warning=FALSE, verbose = FALSE}
library(raster)
library(sp)
library(rgdal)
library(mapview)
library(jsonlite)
library(sp)

library(lattice)
library(latticeExtra)
library(RColorBrewer)

setwd("C:\\Users\\Luise\\Documents\\Universität\\Data Management\\DM\\Daten\\Datensaetze")
raster <- raster("LC82100502014328LGN00_B3.tif")
vector_utm<-readOGR(".","data_2014_subset1", verbose = FALSE)
```


```{r}
plot_vec_grd <- function(raster, vector_utm,vec_attr, vec_col="Greens", ticks= 8){

#Festlegen der Abstände für die Kontraststreckung des Rasters  
min <- max(mean(getValues(raster)) - sd(getValues(raster)), 0)
max <- mean(getValues(raster)) + sd(getValues(raster))
breaks <- seq(min, max, length.out = 256)

#Umprojizierung der Vektor-Datei in das CRS des Rasters und festelgen der Legende-Klassen sowie Farben
vector_utm<- spTransform(vector_utm, CRS(projection(raster)))
vector_classes <- cut(na.omit(vector_utm@data[,colnames(vector_utm@data)==vec_attr]),
c(seq(0,max(na.omit(vector_utm@data[,colnames(vector_utm@data)==vec_attr])),
by=max(na.omit(vector_utm@data[,colnames(vector_utm@data)==vec_attr]))/6)))
vector_colors <- colorRampPalette(brewer.pal(6,vec_col))(6)

#Generierung der Ticks für die Koordinatenlinien
yat = seq(extent(raster)@ymin, 
          extent(raster)@ymax, length.out = ticks)
xat = seq(extent(raster)@xmin, 
          extent(raster)@xmax, length.out = ticks)

#Generierung des Raster-Plots mit Koordinatenlinien und Legende
plt <- spplot(raster, col.regions = gray.colors(256), at = breaks,
              key = list(space = 'left', text = list(levels(vector_classes)), 
                         points = list(pch = 21, cex = 2, fill = vector_colors)),
              colorkey=list(space="right"),
              panel = function(...){
                panel.levelplot(...)
                panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
              },
              scales = list(x = list(at = xat),
                            y = list(at = yat)))

#Generierung des Vektor-Plots 
orl <- spplot(vector_utm, zcol = vec_attr, col.regions = vector_colors, 
              cuts = c(seq(0,max(na.omit(vector_utm@data[,colnames(vector_utm@data)==vec_attr])),
                           by=max(na.omit(vector_utm@data[,colnames(vector_utm@data)==vec_attr]))/6)))

#Rückgabe des Gesamtplots
return(plt + as.layer(orl))
}
```




```{r}

inputPanel(
  sliderInput("gridbar", label = "Number of Grids",min= 2,max= 10, value = 1,step= 1),
 
  
  selectInput("colors", label = "Color of Map",
              choices =c("Greens","Blues", "Reds"),selected = "Reds" ),

  

  selectInput("attributes",label = "Attributes",
               choices = names(vector_utm), selected = "ANIMALS")
)

renderPlot(

plot_vec_grd(raster = raster ,vector_utm = vector_utm ,vec_attr = input$attributes, vec_col= input$colors, ticks= input$gridbar)
  
)
```






