---
title: "Visualize Spatial Data"
author: "Max"
date: "December 16, 2015"
output: html_document
---

### Introduction ###

This short tutorial shows how to write a function that visualizes a spatial 
point vector attribute over a contrast stretched raster image, a discrete legend 
for the attribute values and a continuous legend for the raster image. As an 
example there will be a Landsat dataset from the November 23rd, 2014, Pico
Pequeno eruption on the island of Fogo, Cape Verde.

### Setup ###

To begin we need to set up your working directory and load the necessary 
libraries for the task.

```{r, message=FALSE}
# Put in your path here:
setwd("/home/max/1.Semester/Data_Management/Projekte/Ebola/Input/Landsat/")

library(sp)
library(rgdal)
library(raster)
library(lattice)
library(latticeExtra)

```

### Load input data ###

Now we load and set our input datasets to certain variables for further 
processing. Due to diffrent proejctions the vectordataset needs to be 
transformed to match the raster prokection.


```{r, results='hide'}
raster <- raster("LC82100502014328LGN00_B3.tif")
vector <- readOGR("data_2014_subset1.shp", layer = "data_2014_subset1")
# Transform vector projection 
vector_utm <- spTransform(vector, CRS(projection(raster)))
```

### Define legend variables ###
Now we start to define our variables for our two legends. for the discrete one 
we need to set vector classes and vector colors. To set up the continous raster 
legend we use its minimal and maximal values as breaks. To achieve a better
map like look we draw lines acrros the raster at certain tics (last two commands)

```{r}
vector_classes <- cut(vector_utm@data$NAT, c(0,1,2,3,4,5,6,7,8,9))
vector_colors <- colorRampPalette(brewer.pal(9,"Greens"))(9)

min <- max(mean(getValues(raster)) - sd(getValues(raster)), 0)
max <- mean(getValues(raster)) + sd(getValues(raster))

breaks <- seq(min, max, length.out = 256)

yat = seq(extent(raster)@ymin, 
          extent(raster)@ymax, length.out = 5)
xat = seq(extent(raster)@xmin, 
          extent(raster)@xmax, length.out = 5)
```

### Visulize the data ###

After defining all necessary variables we are now able to visulize our map. For 
this we stack at first the raster and grid line layers in one plot 
using the "panel" function.

```{r}
plt <- spplot(raster, col.regions = gray.colors(256), at = breaks,
              key = list(space = 'left', text = list(levels(vector_classes)), 
                         points = list(pch = 21, cex = 2, fill = vector_colors)),
              colorkey=list(space="right"),
              panel = function(...){
                panel.levelplot(...)
                panel.abline(h = yat, v = xat, col = "grey0", lwd = 0.8, lty = 3) 
              },
              scales = list(x = list(at = xat),
                            y = list(at = yat)))
```

In the next step we plot the vector data using a simple plot function. Every
class has its color as set up above.

```{R}
orl <- spplot(vector_utm, zcol = "NAT", col.regions = vector_colors, 
              cuts = c(0,1,2,3,4,5,6,7,8,9))
```

Now we only need to combine both plots in one to visulize our final 
map.

```{R}
finalplot <- plt + as.layer(orl)
```

Finally, we are able to plot the final result

```{R, echo=FALSE}
finalplot
```
```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Here is the another function

```{r, echo=FALSE}
plot(cars, col ="green")
```

